### 2019-04-23 Sections/verification_of_cloud_quantum_computing.tex
ZKP prob desc

ZKPs are useful in a number of cryptographic applications, most notably in authentication\index{Authentication}. In the case of classical computing, a variety of free software packages are available for compiling ZKPs for generic code. However, ZKPs become far more valuable in the case of cloud quantum computing, where there is an inherent complexity asymmetry between the client Victor (classical resources only) and the server Peggy (full quantum resources), whereby efficient ZKPs become a useful transactional tool during computational outsourcing. In a commercial context, a client can convince themselves that a server has actually performed an outsourced computation before finalising the transaction.

>>>>

ZKPs are useful in a number of cryptographic applications, most notably in authentication\index{Authentication}. In the case of classical computing, a variety of free software packages are available for compiling ZKPs for generic code. However, ZKPs become far more valuable in the case of cloud quantum computing, where there is an inherent complexity asymmetry between the client Victor (classical resources only) and the server Peggy (full quantum resources), whereby efficient ZKPs become a useful transactional tool during computational outsourcing. In a commercial context, a client can convince themselves that a server has actually performed an outsourced computation before finalising the transaction. The problem description for this scenario is shown in Fig.~\ref{fig:ZKP_problem_description}.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{ZKP_problem_description}	
	\captionspacefig \caption{Problem description for using zero-knowledge proofs as a tool in the commercial outsourcing of quantum problems provided by a classical client (limited to both classial computation and communication) to a quantum-capable server. The proof provided by the server demonstrates that the client's computation has been faithfully executed, without disclosing the outcome before finalising the commercial transaction.}\label{fig:ZKP_problem_description}
\end{figure}
